Optimal (Multiway) Spatial Joins

### 2024-06-04 msj.tex
yufei

\extraspacing \underline{\em Proof of Statement (2).} Take any $k$-tuple $(r_1, ..., r_{k-2}, h, v) \in \J_2$. Define $h'$ as the trimmed segment of $h$, and point $p = h \cap v$. We first argue that the $(k-1)$-tuple $\bm{t} = (r_1, ..., r_{k-3}, h', v)$ belongs to $\J(R_1,...,R_{k-3}, H', V)$, or equivalently, the point $h' \cap v$ falls in all of $r_1,...,r_{k-3}$. The subsequent discussion will show that $h' \cap v$ is in fact the same point as $p = h \cap v$. From $(r_1,...,r_{k-2},h,v) \in \J(R_1,...,R_{k-2},H,V)$, we already know that $p$ falls in all of $r_1,...,r_{k-2}$. It will then follow that $r_1,...,r_{k-3}$ all cover $h' \cap v$.

@@

As $h'$ is contained in $h$, for proving $h' \cap v = p$, it suffices to explain why $p$ is on $h'$. Let us represent $h$ as $[x_1,x_2] \times y$. Accordingly, the segment $h'$ can be written as $[x_1, x_2'] \times y$ for some $x_2' \in [x_1, x_2]$. By the definition of a trimmed segment, $(x_2',y)$ is the rightmost point on $h$ that falls in a left-end covering rectangle of $h$ in $R_{k-2}$. As $(r_1,...,r_{k-2},h,v) \in \J_2$, we know that $r_{k-2}$ is a left-end covering rectangle of $h$, and $r_{k-2}$ covers $p$. Therefore, the x-coordinate of $p$ cannot exceed $x_2'$, allowing us to assert that $p$ is on $h'$.

>>>>

\extraspacing \underline{\em Proof of Statement (2).} Take any $k$-tuple $(r_1, ..., r_{k-2}, h, v) \in \J_2$. Set $p = h \cap v$, and define $h'$ as the trimmed segment of $h$. We first argue that the $(k-1)$-tuple $\bm{t} = (r_1, ..., r_{k-3}, h', v)$ belongs to $\J(R_1,...,R_{k-3}, H', V)$, or equivalently, the point $h' \cap v$ falls in all of $r_1,...,r_{k-3}$. The subsequent discussion will show that $h' \cap v$ is in fact the same point as $p = h \cap v$. From $(r_1,...,r_{k-2},h,v) \in \J(R_1,...,R_{k-2},H,V)$, we already know that $p$ falls in all of $r_1,...,r_{k-2}$. It will then follow that $r_1,...,r_{k-3}$ all cover $h' \cap v$.

@@

As $h'$ is contained in $h$, for proving $h' \cap v = p$, it suffices to explain why $p$ is on $h'$. Let us represent $h$ as $[x_1,x_2] \times y$. Accordingly, the segment $h'$ can be written as $[x_1, x_2'] \times y$ for some $x_2' \in [x_1, x_2]$. By the definition of a trimmed segment, $(x_2',y)$ is the rightmost point on $h$ that falls in a left-end covering rectangle of $h$ in $R_{k-2}$. As $(r_1,...,r_{k-2},h,v) \in \J_2$, we know that $r_{k-2}$ is a left-end covering rectangle of $h$, and $r_{k-2}$ covers $p$ (which is a point on $h$). Therefore, the x-coordinate of $p$ cannot exceed $x_2'$, allowing us to assert that $p$ is on $h'$.
